---
title: "Data - Partitions time and memory size"
author: "Pablo Morala"
date: '2022-07-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tictoc)
```


This file generates the partitions needed for the figures in `Figures - Polynomial terms N and partitions size and time.Rmd`, storing their generation times and memory size for several values of $p$ and $Q$.  This is donde both for all possible partitions (Part 1) and then using the equivalent partitions trick to only generate some of them (Part 2).

So they are comparable, both are implemented in C++ and will use the same values for $p$ and $Q$:

```{r}
# Chose values for p and Q
p_vec <- c(4,5,6)
Q_vec <- c(4,6,8,10)
```


# All partitions


```{r}

# Clear log times and start counting the total time
tic.clearlog()
tic("total")
for (Q in Q_vec){
  for (p in p_vec){
    tic(paste("all_partitions_full",
                           "p", p,
                           "Q", Q,
                           sep = "_"))
    all_partitions <- nn2poly:::generate_partitions_full(p, Q)

    # Generate a name to store the simulation file,
    name <- paste("temporal/all_partitions_full",
                             "p", p,
                             "Q", Q,
                             sep = "_")
    print(name)
    
    # Save simulation data
    saveRDS(all_partitions, name)
    toc(log = TRUE, quiet = FALSE)
    rm(all_partitions)
  }
}
toc(log = TRUE, quiet = FALSE)

log.txt <- tic.log(format = TRUE)
log.lst <- tic.log(format = FALSE)

# Store de time values from the tictoc logs:
name_time_logs_txt <- paste("temporal/timelogs_full_with",
                                   "max_p", p_vec[length(p_vec)],
                                   "max_Q", Q_vec[length(Q_vec)],
                                   "txt",
                                   sep = "_")


# Save logs:
saveRDS(log.txt, name_time_logs_txt)


```



# Partitions of equivalent multisets


```{r}

# Clear log times and start counting the total time
tic.clearlog()
tic("total")
for (Q in Q_vec){
  for (p in p_vec){
    tic(paste("all_partitions_equivalent",
                           "p", p,
                           "Q", Q,
                           sep = "_"))
    all_partitions <- nn2poly:::generate_partitions(p, Q)

    # Generate a name to store the simulation file,
    name <- paste("temporal/all_partitions_equivalent",
                             "p", p,
                             "Q", Q,
                             sep = "_")
    print(name)
    
    # Save simulation data
    saveRDS(all_partitions, name)
    toc(log = TRUE, quiet = FALSE)
    rm(all_partitions)
  }
}
toc(log = TRUE, quiet = FALSE)

log.txt <- tic.log(format = TRUE)
log.lst <- tic.log(format = FALSE)

# Store de time values from the tictoc logs:
name_time_logs_txt <- paste("temporal/timelogs_equivalent_with",
                                   "max_p", p_vec[length(p_vec)],
                                   "max_Q", Q_vec[length(Q_vec)],
                                   "txt",
                                   sep = "_")

# Save logs:
saveRDS(log.txt, name_time_logs_txt)


```